Recurrent Neural Networks

### 2017-12-10 paper/paper.tex
"data set" -> "dataset"

	In this practice we explore the effects of the different elements of RNNs using a specific data set\footnote{https://upc-mai-dl.github.io/rnn-lab-autonomous/}. In this case we extend the Wind prediction example that we used in the previous guided session.

@@

		\item [Complementary sites] In the original experiment we predicted the wind speed using the data from one site, but the data set includes three additional sites that are geographically close (they are in the vertices of a 2 km square). Here we leverage the information of the wind speed from the other sites.

@@

	In the guided laboratory we trained the model with 50,000 samples, validated with 10,000 and tested with 10,000. In this practice we use the whole data set, training our model with 122,736 samples, validating with 61,368 and testing with 61,368 for no apparent reason\footnote{Actually, the reason behind this decision is just that we performed some dummy tests using the whole data set and we forgot to set the default value again.}.

@@

		\item We suspect that in this data set there are no data relations over long intervals of time, hence we will not obtain a better result by increasing the window size. However, decreasing it may lead to a worse accuracy.
	\end{itemize}

>>>>

	In this practice we explore the effects of the different elements of RNNs using a specific dataset\footnote{https://upc-mai-dl.github.io/rnn-lab-autonomous/}. In this case we extend the Wind prediction example that we used in the previous guided session.

@@

		\item [Complementary sites] In the original experiment we predicted the wind speed using the data from one site, but the dataset includes three additional sites that are geographically close (they are in the vertices of a 2 km square). Here we leverage the information of the wind speed from the other sites.

@@

	In the guided laboratory we trained the model with 50,000 samples, validated with 10,000 and tested with 10,000. In this practice we use the whole dataset, training our model with 122,736 samples, validating with 61,368 and testing with 61,368 for no apparent reason\footnote{Actually, the reason behind this decision is just that we performed some dummy tests using the whole dataset and we forgot to set the default value again.}.

@@

		\item We suspect that in this dataset there are no data relations over long intervals of time, hence we will not obtain a better result by increasing the window size. However, decreasing it may lead to a worse accuracy.
	\end{itemize}
